The Rockerverse: Images, Packages, and Applications for Containerization with R

### 2020-01-23 manuscript.Rmd
combine rc and audit section, see #64 #43

## Research Compendia
\label{compendia}

Containers provide a high degree of isolation that is often desirable when attempting to capture a specific computational environment so that others can reproduce and extend a research result.
Many computationally intensive research projects depend on specific versions of original and third-party software packages in diverse languages, joined together to form a pipeline through which data flows.
New releases of even just a single piece of software in this pipeline can break the entire workflow, making it difficult to find the error and difficult for others to reuse existing pipelines.
These breakages can make the original the results irreproducible and not extandable.
The chance of a substantial disruption like this is high in a multi-year research project where key pieces of third-party software may have several major updates over the duration of the project.
The classical "paper" article is insufficient to adequately communicate the knowledge behind such research projects \citep[cf.][]{donoho_invitation_2010,marwick_how_2015}.
\citet{gentleman_statistical_2007} coined the term _Research Compendium_ for a dynamic document together with supporting data and code.
They use the R package system \cite{core_writing_1999} as the functional prototype for structuring, validation, and distribution of research compendia.
This concept has been taken up and extended\footnote{See full literature list at \href{https://research-compendium.science/}{https://research-compendium.science/}.}, not the least by applying containerisation and other methods for managing computing environments---see Section&nbsp;\nameref{envs}.
Containers give the researcher an isolated environment to assemble these research pipelines with specific versions of software.
Research workflows in containers are safe from contamination from other activities occuring on the researcher's computer, for example the installation of newest version of packages for teaching demonstrations.
Given the users in this scenario, i.e., often academics with limited formal software development training, templates and assistance with containers around research compendia is essential.

@@

## Publication Reproducibility Audits

A recommendation of the recent National Academies' report on _Reproducibility and Replicability in Science_ is that journals "consider ways to ensure computational reproducibility for publications that make claims based on computations" \citep{NASEM2019}.
In fields such as Political Science and Economics, journals are increasingly adopting policies requiring authors to publish the code and data required to reproduce computational findings reported in published manuscripts, subject to independent verification \citep{Jacoby2017,Vilhuber2019,Alvarez2018,Christian2018,Eubank2016,King1995}.
Problems with the computational environment, installation and availability of software dependencies are common. R is gaining popularity in these communities (in a sample of 105 replication packages published by the _American Journal of Political Science_ (AJPS) over 65% use R). 
The NSF-funded Whole Tale project uses the Rocker Project community images with the goal of improving the reproducibility of published research artifacts and simplifying the publication and verification process for both authors and journals by reducing errors and time spent specifying the environment.

>>>>

## Packaging research reproducibly
\label{compendia}

Containers provide a high degree of isolation that is often desirable when attempting to capture a specific computational environment so that others can reproduce and extend a research result.
Many computationally intensive research projects depend on specific versions of original and third-party software packages in diverse languages, joined together to form a pipeline through which data flows.
New releases of even just a single piece of software in this pipeline can break the entire workflow, making it difficult to find the error and difficult for others to reuse existing pipelines.
These breakages can make the original the results irreproducible and not extandable.
The chance of a substantial disruption like this is high in a multi-year research project where key pieces of third-party software may have several major updates over the duration of the project.
The classical "paper" article is insufficient to adequately communicate the knowledge behind such research projects \citep[cf.][]{donoho_invitation_2010,marwick_how_2015}.
\citet{gentleman_statistical_2007} coined the term **Research Compendium** for a dynamic document together with supporting data and code.
They use the R package system \cite{core_writing_1999} as for the functional prototype to structuring, validation, and distribution of research compendia.
This concept has been taken up and extended\footnote{See full literature list at \href{https://research-compendium.science/}{https://research-compendium.science/}.}, not the least by applying containerisation and other methods for managing computing environments---see Section&nbsp;\nameref{envs}.
Containers give the researcher an isolated environment to assemble these research pipelines with specific versions of software.
Research workflows in containers are safe from contamination from other activities occuring on the researcher's computer, for example the installation of newest version of packages for teaching demonstrations.
Given the users in this scenario, i.e., often academics with limited formal software development training, templates and assistance with containers around research compendia is essential.

@@

A recommendation of the recent National Academies' report on _Reproducibility and Replicability in Science_ is that journals _"consider ways to ensure computational reproducibility for publications that make claims based on computations"_ \citep{NASEM2019}.
In fields such as Political Science and Economics, journals are increasingly adopting policies requiring authors to publish the code and data required to reproduce computational findings reported in published manuscripts, subject to independent verification \citep{Jacoby2017,Vilhuber2019,Alvarez2018,Christian2018,Eubank2016,King1995}.
Problems with the computational environment, installation and availability of software dependencies are common.
R is gaining popularity in these communities, such as creating a research compendium.
In a sample of 105 replication packages published by the _American Journal of Political Science_ (AJPS) over 65% use R.
The NSF-funded Whole Tale project uses the Rocker Project community images with the goal of improving the reproducibility of published research artifacts and simplifying the publication and verification process for both authors and journals by reducing errors and time spent specifying the environment.
